Algomusicology, ????, Profit

### 2016-05-22 paper.tex
Fix single quotes.

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings. We might just as easily have
used the letters 'G', 'A', 'T' and 'C' to generate every possible DNA sequence.

@@

In Carl Sagan's novel 'Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
If we design an appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However,
we would encounter a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want
is in there somewhere, but we don't know where to look.

@@

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track 'Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
of "repetitive beats".

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song
'Got to Give It Up'\cite{Got to Give It Up, USA Today}.

@@

As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.~\footnote{The encoding scheme is chosen
to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the appendix and the accompanying code.}

@@

There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to 'Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system.

>>>>

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings. We might just as easily have
used the letters `G', `A', `T' and `C' to generate every possible DNA sequence.

@@

In Carl Sagan's novel `Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
If we design an appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However,
we would encounter a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want
is in there somewhere, but we don't know where to look.

@@

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track `Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
of "repetitive beats".

@@

`Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song
`Got to Give It Up'\cite{Got to Give It Up, USA Today}.

@@

As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
is the value of \verb|skip-to| that results in a passable version of `Blurred Lines'.~\footnote{The encoding scheme is chosen
to be reversible, which allowed me to determine where in the Champernowne word `Blurred Lines' would occur. Full details are in the appendix and the accompanying code.}

@@

There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to `Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system.
